Reviewer comments from PeerJ

### 2015-03-23 PeerJResponse.tex
edits to response

\noindent Dear Dr.Vision and editorial staff at \emph{PeerJ}, \\

@@

\res{We have addressed comments from Reviewer 2 regarding the validity of the PCR assays. Sequencing of PCR products were not sequenced, but primer combinations for each of the 2 PCRs produced the expected sized bands. Primers were designed using previously sequenced teosinte and maize sequences provided by John Doebley, and were initially tested in both maize and teosinte for validity.  We have clarified this point in the text page 4, lines 75-87 and have added additional labeling to the gel image (Figure 2).}

>>>>

\noindent Dear Dr. Vision and editorial staff at \emph{PeerJ}, \\

@@

\res{We have addressed comments from Reviewer 2 regarding the validity of the PCR assays. PCR products were not sequenced, but primer combinations for both PCR assays produced only the expected sized bands. Primers were designed using previously sequenced teosinte and maize sequences provided by John Doebley and were initially tested in both maize and teosinte for validity.  We have clarified this point in the text page 4, lines 75-87 and have added additional labeling to the gel image (Figure 2).}
